A-maze of Natural Stories: Texts are comprehensible using the Maze task

### 2022-08-19 Papers/Paper/manuscript.Rmd
move file

comp_comp <- read_rds(here("Analysis/comp.rds")) %>% 
  filter(source %in% c(">80% correct","<80% correct", "SPR 1st story"))

comp_tally <- read_rds(here("Analysis/comp.rds")) %>% group_by(source) %>% filter(correct>4) %>% 
  summarize(good=round(sum(pct)*100))
comp_plot <- ggplot(comp_comp, aes(x=correct,y=pct,fill=source))+
  geom_col(position="dodge")+
  facet_grid(.~source)+
  labs(x="Comprehension questions correct (out of 6)", y="Percent participants")+
  scale_fill_manual(values=c(">80% correct"="darkgreen","<80% correct"="darkred",  "SPR 1st story"="grey30"))+
guides(fill="none")

>>>>

comp_comp <- read_rds(here("Analysis/models/comp.rds")) %>% 
  filter(source %in% c(">80% correct","<80% correct", "SPR 1st story"))

comp_tally <- read_rds(here("Analysis/models/comp.rds")) %>% group_by(source) %>% filter(correct>4) %>% 
  summarize(good=round(sum(pct)*100))
comp_plot <- ggplot(comp_comp, aes(x=correct,y=pct,fill=source))+
  geom_col(position="dodge")+
  facet_grid(.~source)+
  labs(x="Comprehension questions correct (out of 6)", y="Percent participants")+
  scale_fill_manual(values=c(">80% correct"="darkgreen","<80% correct"="darkred",  "SPR 1st story"="grey30"))+
guides(fill="none")
